The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-08-17 paper.tex
combine the antenna layout and psf plots

Additionally we can pre-compute the Cholesky decomposition of $\b B^*\b B + \varepsilon\b I = \b
U^*\b U$, where $\b U$ is an upper-triangular matrix. Inverting an upper triangular matrix is an
$\mathcal{O}(N^2)$ operation (instead of $\mathcal{O}(N^3)$ for a general matrix inverse).\footnote{
    Inverting a matrix is numerically unstable and should be avoided. Instead of computing $\b
    U^{-1}$, the linear equation $\b U\b x = \b y$ is solved each time the matrix inverse is needed.
}
Equation~\ref{eq:psf} can then be rapidly evaluated from right to left as:
\begin{equation}\label{eq:rapid-psf}
    \b a_\text{PSF} =
        \b U^{-1}\,\big(\b U^*\big)^{-1}\,\big(\b B^*\b B\big)\,\b a_\text{PS}\,.
\end{equation}
Furthermore, Equation~\ref{eq:rapid-psf} does not need to be separately evaluated for each CLEAN
component. Instead we can identify $N$ CLEAN components, accumulate $\b a_\text{PS}$ for each
component, and evaluate Equation~\ref{eq:rapid-psf} on the accumulation. This can greatly reduce the
number of times this equation needs to be evaluated, but care must be taken to ensure that the $N$
components are not so close together that sidelobes from one may interact with another.

@@

\begin{figure}[t]
    \plotone{figures/antenna-layout/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

\begin{figure}[t]
    \plotone{figures/psf/spw04-psf-45-degrees}
    \caption{
        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
        declination of $+45^\circ$ and frequency of $36.528$ MHz.
    }
    \label{fig:psf}
\end{figure}

@@

The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
placed outside of the core in order to extend the maximum baseline length to $\sim$1.5 km. The final
5 antennas are equipped with noise-switched front ends for calibrated total power measurements of
the global sky brightness.  These antennas are used as part of the LEDA experiment
\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.
Figure~\ref{fig:antenna-layout} is a diagram of the antenna configuration.

>>>>

Additionally we can pre-compute the Cholesky decomposition of $\b B^*\b B + \varepsilon\b I = \b
U^*\b U$, where $\b U$ is an upper-triangular matrix. Inverting an upper triangular matrix is an
$\mathcal{O}(N^2)$ operation (instead of $\mathcal{O}(N^3)$ for a general matrix inverse).\footnote{
    Inverting a matrix is numerically unstable and should be avoided. Instead of computing $\b
    A^{-1}$, the linear equation $\b A\b x = \b b$ is solved each time the matrix inverse is needed.
}
Equation~\ref{eq:psf} can then be rapidly evaluated from right to left as:
\begin{equation}\label{eq:rapid-psf}
    \b a_\text{PSF} =
        \b U^{-1}\,\big(\b U^*\big)^{-1}\,\big(\b B^*\b B\big)\,\b a_\text{PS}\,.
\end{equation}
Furthermore, Equation~\ref{eq:rapid-psf} does not need to be separately evaluated for each CLEAN
component. Instead we can identify $N$ CLEAN components, accumulate $\b a_\text{PS}$ for each
component, and evaluate Equation~\ref{eq:rapid-psf} on the accumulation. This can greatly reduce the
number of times this equation needs to be evaluated, but care must be taken to ensure that the $N$
components are not so close together that sidelobes from one may interact with another.

@@

\begin{figure*}[t]
    \includegraphics[width=\textwidth]{figures/psf/psf}
    \caption{
        \textbf{(left panel)}
        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
        \textbf{(middle panel)}
        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
        declination of $+45^\circ$ and frequency of $36.528$ MHz.
        \textbf{(right panel)}
        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
        declination of $+45^\circ$ and frequency of $73.152$ MHz.
    }
    \label{fig:psf}
\end{figure*}

@@

The 288 antennas are arranged in a pseudo-random configuration optimized to minimize sidelobes in
snapshot imaging.  251 of the antennas are contained within a 200 m diameter core. 32 antennas are
placed outside of the core in order to extend the maximum baseline length to $\sim$1.5 km. The final
5 antennas are equipped with noise-switched front ends for calibrated total power measurements of
the global sky brightness.  These antennas are used as part of the LEDA experiment
\citep{todo_price_2017} to measure the global signal of 21 cm absorption from the cosmic dawn.  The
left panel of Figure~\ref{fig:psf} is a diagram of the antenna configuration.
